##Practical Machine Learning Project
###Loading require packages
```{r}
library(data.table)
library(dplyr)
library(caret)
library(randomForest)
```
###Loading Data
```{r}
fileUrl="https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
download.file(fileUrl,destfile="e:/uconn/academic/coursera/Practical Machine Learning/ProjectTrain.csv")
fileUrl="https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
download.file(fileUrl,destfile="e:/uconn/academic/coursera/Practical Machine Learning/ProjectTest.csv")
Train<-read.csv("e:/uconn/academic/coursera/Practical Machine Learning/ProjectTrain.csv")
Test<-read.csv("e:/uconn/academic/coursera/Practical Machine Learning/ProjectTest.csv")
```
###Delete missing value
```{r}
Missing <- sapply(Test, function (x) any(is.na(x) | x == ""))
Predictor <- names(Test)[!Missing & grepl("belt|arm|dumbbell|forearm", names(Missing))]
Predictor
Train<-Train[,c("classe",Predictor)]
```
###Devide train data into training data and testing data
```{r}
inTrain<-createDataPartition(y=Train$classe,p=0.7,list=FALSE)
training<-Train[inTrain,]
testing<-Train[-inTrain,]
```
###Checking correlation between variable and listed highly correlated data
```{r which}
M<-abs(cor(training[,-1]))
diag(M)<-0
which(M>0.8,arr.ind=T)
```
###Preprocessing with centering and scaling
```{r}
PreObj<-preProcess(training[,-1])
trainingSD<-predict(PreObj,training[,-1])
```
###Preprocessing with PCA with a explaination of 80% variance
```{r}
preProc<-preProcess(trainingSD,method="pca",thresh=0.8)
trainingPC<-predict(preProc,trainingSD)
```
###Training data with random forest
```{r}
modFit<-randomForest(training$classe~.,data=trainingPC)
```
###Listing training data's confusion matrix
```{r}
pred<-predict(modFit,trainingPC,type="class")
training$predictRight<-pred==training$classe
table(pred,training$classe)
```
###Listing testing data's confusion matrix
```{r}
testingSD<-predict(PreObj,testing[,-1])
testingPC<-predict(preProc,testingSD)
predTest<-predict(modFit,testingPC,type="class")
testing$predictRight<-predTest==testing$classe
table(predTest,testing$classe)
```
###Applied model to test data
```{r}
Test<-Test[,Predictor]
testSD<-predict(PreObj,Test)
testPC<-predict(preProc,testSD)
answer<-predict(modFit,testPC,type="class")
```